Discrete Quantum Theories and Computing

### 2019-04-22 dissertation.tex
dissertation.lyx Replaced URLs from \code to \url...

%% LyX 2.3.2-2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[11pt,twoside]{iuphd}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fontspec}
\setmainfont[Mapping=tex-text]{Times New Roman}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\usepackage{verbatim}
\usepackage{rotfloat}
\usepackage{booktabs}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage[all]{xy}

@@

\begin{preface*}
\begin{itemize}
\item The latest PDF version of this thesis is in GitHub: \code{https://git.io/fxbuG}.
\item Its source code is typeset using \LyX{} \cite{LyX} in \code{https://git.io/fxbuE}
and the exported \LaTeX{} file is in \code{https://git.io/fhZBW}.
\item Any comments can be left in the Issue part of the GitHub repository:
\code{https://git.io/fxbug}.
\end{itemize}
Following explains how to compile the PDF from the \LaTeX{} source:
\begin{enumerate}
\item \label{enu:Clone-the-git}Clone the git repository of this thesis
\code{https://git.io/fhZP5} into your local directory and the thesis
document class \code{https://github.com/yuttai/iuphd} in a location
where the system can find.
\item In the local directory of this thesis, run \code{xelatex dissertation.tex}.
\item Run \code{biber dissertation}.
\item Run \code{xelatex dissertation.tex} several times until all the references
are resolved.
\end{enumerate}
The previous steps only tested in Microsoft Windows with MiK\TeX{}
2.9. Please report me if there is any difficulty to compile it. Besides,
to compile a PDF file from the \LyX{} source, just finish step~\ref{enu:Clone-the-git},
open \code{dissertation.lyx} in \LyX , and click the toolbar button
\includegraphics[width=1em]{buffer-view}.\end{preface*}

@@

\begin{definition}[IVPM]Assume a collection of intervals $\mathscr{I}$
including $\imposs$ and $\necess$ with addition and scalar multiplication
defined as follows: \begin{subequations}\label{eq:interval-operations}
\begin{eqnarray}
 &  & [\ell_{0},r_{0}]+[\ell_{1},r_{1}]=[\ell_{0}+\ell_{1},r_{0}+r_{1}]\textrm{ and}\\
 &  & x[\ell,r]=\begin{cases}
[x\ell,xr] & \textrm{for }x\ge0\,;\\{}
[xr,x\ell] & \textrm{for }x\le0\,.
\end{cases}\label{eq:interval-times}
\end{eqnarray}
\end{subequations} Given a finite sample space~$\Omega$, and its
power set~$2^{\Omega}$ as the classical event space, a classical
IVPM~$\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$ is a function
subject to the following constraints:\begin{subequations}\label{eq:CIVPM-constraints}
\begin{eqnarray}
 &  & \bar{\mu}(\emptyset)=\imposs\,,\\
 &  & \bar{\mu}(\Omega)=\necess\,,\label{eq:CIVPM-necess}\\
 &  & \bar{\mu}\left(\overline{E}\right)=\necess-\bar{\mu}\left(E\right)\,,\label{eq:CIVPM-complement}
\end{eqnarray}
\end{subequations} and satisfying the convexity condition, Eq.~(\ref{eq:classicalconvex}),
for each pair of events~$E_{0}$ and~$E_{1}$.\end{definition}

@@

\begin{proof}The proof follows the outline of the proof of the classical
inclusion-exclusion principle. From the commuting projectors $P_{0}$
and $P_{1}$, we construct the following three orthogonal projectors:
$P_{0}P_{1}$, $P_{0}\left(\mathbb{1}-P_{1}\right)$, and $\left(\mathbb{1}-P_{0}\right)P_{1}$.
Then we proceed as follows:

\noindent 
\begin{equation*} 
\begin{aligned} 
\noalign{$\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)$} 
\qquad\qquad=~~&\bar{\mu}\left(P_{0}P_{1}+P_{0}(\mathbb{1}-P_{1})+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)  
 & (\mbox{because } P_{0} = P_{0}P_{1}+P_{0}(\mathbb{1}-P_{1})) \\ 
=~~& \bar{\mu}\left(P_{0}(\mathbb{1}-P_{1})+P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right) \\ 
=~~& \bar{\mu}\left(P_{0}(\mathbb{1}-P_{1})+P_{0}P_{1}+(\mathbb{1}-P_{0})P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)  
     & (\mbox{because } P_{1} = P_{0}P_{1}+(\mathbb{1}-P_{0})P_{1}) \\ 
=~~& \bar{\mu}(P_{0}(\mathbb{1}-P_{1}))+\bar{\mu}(P_{0}P_{1})+\bar{\mu}((\mathbb{1}-P_{0})P_{1})+ 
   \bar{\mu}\left(P_{0}P_{1}\right) & (\mbox{using Eq.~(\ref{amr}) twice}) \\ 
=~~& \bar{\mu}(P_{0}(\mathbb{1}-P_{1})+P_{0}P_{1})+\bar{\mu}((\mathbb{1}-P_{0})P_{1}+P_{0}P_{1}) & (\mbox{using Eq.~(\ref{amr}) twice}) \\ 
=~~& \bar{\mu}(P_{0}) + \bar{\mu}(P_{1}) 
\end{aligned} 
\end{equation*}
\end{proof}

@@

When both $\barmuD\left(P'\right)$ and $\barmuD\left(P''\right)$
are $\imposs$, we have both $\bar{\mu}\left(P'\right)$ and $\bar{\mu}\left(P''\right)\subseteq\left[0,\delta\right]$
which implies $\bar{\mu}\left(P'+P''\right)\subseteq\left[0,2\delta\right]$.
Since we assume $\delta<\frac{1}{3}$, the intervals $\left[0,2\delta\right]$
and $\left[1-\delta,1\right]$ are disjoint, which implies $\bar{\mu}\left(P'+P''\right)$
and $\left[1-\delta,1\right]$ are disjoint. Together with the fact
that $\bar{\mu}\left(P'+P''\right)$ is a subset of either $\left[0,\delta\right]$
or $\left[1-\delta,1\right]$, $\bar{\mu}\left(P'+P''\right)$ must
be a subset of $\left[0,\delta\right]$, which implies $\barmuD\left(P'+P''\right)=\imposs$,
and hence also Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal})
is again satisfied.\end{proof}

>>>>

%% LyX 2.3.2-2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[11pt,twoside]{iuphd}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fontspec}
\setmainfont[Mapping=tex-text]{Times New Roman}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\usepackage{verbatim}
\usepackage{rotfloat}
\usepackage{booktabs}
\usepackage{mathrsfs}
\usepackage{url}
\usepackage{enumitem}
\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage[all]{xy}

@@

\begin{preface*}
\begin{itemize}
\item The latest PDF version of this thesis is in GitHub: \url{https://git.io/fxbuG}.
\item Its source code is typeset using \LyX{} \cite{LyX} in \url{https://git.io/fxbuE}
and the exported \LaTeX{} file is in \url{https://git.io/fhZBW}.
\item Any comments can be left in the Issue part of the GitHub repository:
\url{https://git.io/fxbug}.
\end{itemize}
Following explains how to compile the PDF from the \LaTeX{} source:
\begin{enumerate}
\item \label{enu:Clone-the-git}Clone the git repository of this thesis
\url{https://git.io/fhZP5} into your local directory and the thesis
document class \url{https://github.com/yuttai/iuphd} in a location
where the system can find.
\item In the local directory of this thesis, run \code{xelatex dissertation.tex}.
\item Run \code{biber dissertation}.
\item Run \code{xelatex dissertation.tex} several times until all the references
are resolved.
\end{enumerate}
The previous steps only tested in Microsoft Windows with MiK\TeX{}
2.9. Please report me if there is any difficulty to compile it. Besides,
to compile a PDF file from the \LyX{} source, just finish step~\ref{enu:Clone-the-git},
open \code{dissertation.lyx} in \LyX , and click the toolbar button
\includegraphics[width=1em]{buffer-view}.\end{preface*}

@@

\begin{definition}[IVPM]Assume a collection of intervals $\mathscr{I}$
including $\imposs$ and $\necess$ with addition and scalar multiplication
defined as follows: \begin{subequations}\label{eq:interval-operations}
\begin{eqnarray}
 &  & [\ell_{0},r_{0}]+[\ell_{1},r_{1}]=[\ell_{0}+\ell_{1},r_{0}+r_{1}]\textrm{ and}\\
 &  & x[\ell,r]=\begin{cases}
[x\ell,xr] & \textrm{for }x\ge0\,;\\{}
[xr,x\ell] & \textrm{for }x\le0\,.
\end{cases}\label{eq:interval-times}
\end{eqnarray}
\end{subequations} Given a finite sample space~$\Omega$, and its
power set~$2^{\Omega}$ as the classical event space, a classical
IVPM $\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$ is a function
subject to the following constraints:\begin{subequations}\label{eq:CIVPM-constraints}
\begin{eqnarray}
 &  & \bar{\mu}(\emptyset)=\imposs\,,\\
 &  & \bar{\mu}(\Omega)=\necess\,,\label{eq:CIVPM-necess}\\
 &  & \bar{\mu}\left(\overline{E}\right)=\necess-\bar{\mu}\left(E\right)\,,\label{eq:CIVPM-complement}
\end{eqnarray}
\end{subequations} and satisfying the convexity condition, Eq.~(\ref{eq:classicalconvex}),
for each pair of events~$E_{0}$ and~$E_{1}$.\end{definition}

@@

\begin{proof}The proof follows the outline of the proof of the classical
inclusion-exclusion principle. From the commuting projectors $P_{0}$
and $P_{1}$, we construct the following three orthogonal projectors:
$P_{0}P_{1}$, $P_{0}\left(\mathbb{1}-P_{1}\right)$, and $\left(\mathbb{1}-P_{0}\right)P_{1}$.
Then we proceed as follows:
\begin{align*}
 & \bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\\
={} & \bar{\mu}\left(P_{0}P_{1}+P_{0}(\mathbb{1}-P_{1})+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right) & (\mbox{because }P_{0}=P_{0}P_{1}+P_{0}(\mathbb{1}-P_{1}))\\
={} & \bar{\mu}\left(P_{0}(\mathbb{1}-P_{1})+P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\\
={} & \bar{\mu}\left(P_{0}(\mathbb{1}-P_{1})+P_{0}P_{1}+(\mathbb{1}-P_{0})P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right) & (\mbox{because }P_{1}=P_{0}P_{1}+(\mathbb{1}-P_{0})P_{1})\\
={} & \bar{\mu}(P_{0}(\mathbb{1}-P_{1}))+\bar{\mu}(P_{0}P_{1})+\bar{\mu}((\mathbb{1}-P_{0})P_{1})+\bar{\mu}\left(P_{0}P_{1}\right) & (\mbox{using Eq.~(\ref{amr}) twice})\\
={} & \bar{\mu}(P_{0}(\mathbb{1}-P_{1})+P_{0}P_{1})+\bar{\mu}((\mathbb{1}-P_{0})P_{1}+P_{0}P_{1}) & (\mbox{using Eq.~(\ref{amr}) twice})\\
={} & \bar{\mu}(P_{0})+\bar{\mu}(P_{1})
\end{align*}
\begin{comment}
\noindent 
\begin{equation*} 
\begin{aligned} 
\noalign{$\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)$} 
\qquad\qquad=~~&\bar{\mu}\left(P_{0}P_{1}+P_{0}(\mathbb{1}-P_{1})+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)  
 & (\mbox{because } P_{0} = P_{0}P_{1}+P_{0}(\mathbb{1}-P_{1})) \\ 
=~~& \bar{\mu}\left(P_{0}(\mathbb{1}-P_{1})+P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right) \\ 
=~~& \bar{\mu}\left(P_{0}(\mathbb{1}-P_{1})+P_{0}P_{1}+(\mathbb{1}-P_{0})P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)  
     & (\mbox{because } P_{1} = P_{0}P_{1}+(\mathbb{1}-P_{0})P_{1}) \\ 
=~~& \bar{\mu}(P_{0}(\mathbb{1}-P_{1}))+\bar{\mu}(P_{0}P_{1})+\bar{\mu}((\mathbb{1}-P_{0})P_{1})+ 
   \bar{\mu}\left(P_{0}P_{1}\right) & (\mbox{using Eq.~(\ref{amr}) twice}) \\ 
=~~& \bar{\mu}(P_{0}(\mathbb{1}-P_{1})+P_{0}P_{1})+\bar{\mu}((\mathbb{1}-P_{0})P_{1}+P_{0}P_{1}) & (\mbox{using Eq.~(\ref{amr}) twice}) \\ 
=~~& \bar{\mu}(P_{0}) + \bar{\mu}(P_{1}) 
\end{aligned} 
\end{equation*}
\end{comment}
\end{proof}

@@

When both $\barmuD\left(P'\right)$ and $\barmuD\left(P''\right)$
are $\imposs$, we have both $\bar{\mu}\left(P'\right)$ and $\bar{\mu}\left(P''\right)\subseteq\left[0,\delta\right]$
which implies $\bar{\mu}\left(P'+P''\right)\subseteq\left[0,2\delta\right]$.
Since we assume $\delta<\frac{1}{3}$, the intervals $\left[0,2\delta\right]$
and $\left[1-\delta,1\right]$ are disjoint, which implies $\bar{\mu}\left(P'+P''\right)$
and $\left[1-\delta,1\right]$ are disjoint. Together with the fact
that $\bar{\mu}\left(P'+P''\right)$ is a subset of either $\left[0,\delta\right]$
or $\left[1-\delta,1\right]$, $\bar{\mu}\left(P'+P''\right)$ must
be a subset of $\left[0,\delta\right]$, which implies $\barmuD(P'+P'')=\imposs$,
and hence also Eq.~(\ref{eq:QuantumInterval-valuedProbability-Equal})
is again satisfied.\end{proof}
